Refinement of Thermostated Molecular Dynamics via Backward Error Analysis

### 2018-06-14 rigid_bodies.tex
Changes in the bibtex file

Due to its low computational cost, the whole procedure described above can be repeated $n$ times with little impact on the overall integration effort.
This makes it feasible to increase the time step $\timestep$ without ruining the accuracy of the NHC part.
In contrast, evaluating the NVE part is expensive for involving force/torque computations and, in addition, its accuracy goes down very quickly as $\timestep$ increases \cite{Davidchack_2010, Silveira_2017}.
A high-order integration scheme\cite{Omelyan_2007, Van_zon_2008} could possibly admit larger time steps, but it would raise both cost and complexity for entailing the computation (or numerical estimation) of force/torque gradients.
Omelyan's processed splitting approach \cite{Omelyan_2008} seems promising, but its extension to the NVT case without doing back-and-forth processing at every time step would require further theoretical development.
Here we choose to take a simpler path, though.
Instead of trying to increase accuracy in the evaluation of $e^{\timestep \Liu{\tiny NVE}}$, we attempt to quantify the implied discretization errors, with which we can both tune the thermostatting procedure and properly weight the sampled configurations when ensemble average are computed.

@@

Finally, we recall that configurations are sampled from a distribution proportional to $e^{-\beta \refined{\Ham{}}}$.
Notwithstanding, it is possible to compute ensemble averages consistent with a distribution proportional to $e^{-\beta \Ham{}}$, which would have been obtained if $\timestep \to 0$.
For this, we simply need to reweight any computed observable $A$ in accordance with \cite{Torrie_1977}
\begin{equation}
\label{eq:reweighting}
%\langle A \rangle_0 = \frac{\sum\limits_{i=1}^{N_s} A(\vt x_i) \exp \left[{\frac{\refined{\Ham{}}(\vt x_i) - {\Ham{}}(\vt x_i)}{k_\text{\tiny B} T}}\right]}{\sum\limits_{i=1}^{N_s} \exp \left[{\frac{\refined{\Ham{}}(\vt x_i) - {\Ham{}}(\vt x_i)}{k_\text{\tiny B} T}}\right] },
\langle A \rangle_0 = \frac{\left\langle A \exp \left({\frac{\refined{\Ham{}} - \Ham{}}{k_\text{\tiny B} T}}\right)\right\rangle_\timestep}{\left\langle \exp \left({\frac{\refined{\Ham{}} - \Ham{}}{k_\text{\tiny B} T}}\right)\right\rangle_\timestep}.
\end{equation}

>>>>

Due to its low computational cost, the whole procedure described above can be repeated $n$ times with little impact on the overall integration effort.
This makes it feasible to increase the time step $\timestep$ without ruining the accuracy of the NHC part.
In contrast, evaluating the NVE part is expensive for involving force/torque computations and, in addition, its accuracy goes down quickly as $\timestep$ increases \cite{Davidchack_2010, Silveira_2017}.
A high-order integration scheme\cite{Omelyan_2007, Van_zon_2008} could possibly admit larger time steps, but it would raise both cost and complexity for entailing the computation (or numerical estimation) of force/torque gradients.
Omelyan's processed splitting approach \cite{Omelyan_2008} seems promising, but its extension to the NVT case without doing back-and-forth processing at every time step would require further theoretical development.
Here we choose to take a simpler path, though.
Instead of trying to increase accuracy in the evaluation of $e^{\timestep \Liu{\tiny NVE}}$, we attempt to quantify the implied discretization errors, with which we can both tune the thermostatting procedure and properly weight the sampled configurations when ensemble average are computed.

@@

Finally, we recall that configurations are sampled from a distribution proportional to $e^{-\beta \refined{\Ham{}}}$.
Notwithstanding, it is possible to compute ensemble averages consistent with a distribution proportional to $e^{-\beta \Ham{}}$, which would have been obtained if $\timestep \to 0$.
For this, we simply need to reweight any computed observable $A$ in accordance with \cite{Torrie_1977}
\begin{equation}
\label{eq:reweighting}
\langle A \rangle_0 = \frac{\left\langle A \exp \left({\frac{\refined{\Ham{}} - \Ham{}}{k_\text{\tiny B} T}}\right)\right\rangle_\timestep}{\left\langle \exp \left({\frac{\refined{\Ham{}} - \Ham{}}{k_\text{\tiny B} T}}\right)\right\rangle_\timestep}.
\end{equation}
